%&latex
\documentclass[8pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	keepspaces=true,
	numbers=left,
	numbersep=5pt,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	tabsize=2
}

\lstset{style=mystyle}

\begin{document}
%+Title
\section{Problem Statement.}
\paragraph{}
Sandra is a strong independant woman. she loves shopping so much that she decided to spend at least S dinars to buy clothes.
\paragraph{}
there are n different dresses each one with a price $p_i$ ($1<=i<=n$).
Help Sandra find the minimum integer k so that whatever index j ($1<=j<=n-k+1$) she chooses it is guaranteed 
that the sum of coins she will collect ($p_j$ + ... + $p_{j+k-1}$) will be greater than or equal to S.
if Sandra can never collect more than the sum S print "impossible"
\section{Input.}
you will be given as input n ($1<=n<=10^5$) the number of dresses. S ($1<=S<=10^6$) the amount she has to spend.
and n numbers $p_i$ ($0<=p_i<=10^5$) representing the price of the i-th dress.
\section{Output.}
print k if it exists and "impossible" if it doesn't exist.

\section{Examples.}
\subsection{example 1}
Input:
\begin{lstlisting}[language=Python]
8 5
1 0 4 5 0 0 2 1
\end{lstlisting}
Output:
\begin{lstlisting}[language=Python]
5
\end{lstlisting}
\subsection{example 2}
Input:
\begin{lstlisting}[language=Python]
6 1
1 1 1 1 1 1
\end{lstlisting}
Output:
\begin{lstlisting}[language=Python]
1
\end{lstlisting}
\subsection{example 3}
Input:
\begin{lstlisting}[language=Python]
4 10
3 1 1 2
\end{lstlisting}
Output:
\begin{lstlisting}[language=Python]
impossible
\end{lstlisting}


\end{document}

